---
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage[normalem]{ulem}
  - \usepackage[utf8]{inputenc}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{titling}
  - \pretitle{\begin{center}
    \includegraphics[width=4in]{images/CSU-Official-wrdmrk-357-617.png}\LARGE\\}
  - \posttitle{\end{center}}
output:
  pdf_document
params:
  title: 'Face Mask or Respirator Particulate Removal Efficiency Test Results of Qualification Testing - '
  id: "c33"
  type: "detailed"
  fldr: "data"
  img: "img"
  tst: "tst"
geometry: "left=2cm,right=2cm,top=0cm,bottom=2cm"
---

---
title: `r paste0(params$title, "M", toupper(params$id))`
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.path = 'figures/',
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  cache = FALSE)
```

\definecolor{c_failed}{RGB}{205,79,57}
\definecolor{c_passed}{RGB}{46,139,87}
\definecolor{grey50}{RGB}{127,127,127}

\renewcommand{\topfraction}{.85}
\renewcommand{\bottomfraction}{.7}
\renewcommand{\textfraction}{.15}
\renewcommand{\floatpagefraction}{.66}
\setcounter{topnumber}{3}
\setcounter{bottomnumber}{3}
\setcounter{totalnumber}{4}

```{r functions_file}
source("functions_n95.R")
```

```{r read_metadata}
# read metadata
meta <- read_metadata(fldr = params$fldr) %>%
  filter(mask == params$id)
```

```{r read_data}
# read data
data <- read_data(fldr = params$fldr, id = params$id, tst = params$tst) %>%
  clean_data()
```

```{r data_average}
# one minute average
data_time <- data %>% group_by(rep) %>%
  summarise(t_min = min(datetime, na.rm = TRUE),
            t_max = max(datetime, na.rm = TRUE)) %>%
  group_by(rep) %>%
  mutate(datetime = list(seq(t_min, t_max, by= 1)), t_min = NULL, t_max = NULL) %>%
  unnest(cols = c(datetime)) %>%
  ungroup() %>%
  select(-rep) %>%
  left_join(data, by = "datetime") %>%
  group_by(rep) %>%
  mutate_at(vars(-group_cols()), zoo::rollmeanr, k = 60, na.pad = TRUE) %>%
  fill(-group_cols()) %>%
  ungroup()
```

```{r data_ref}
# extract reference data
data_ref <- data_time %>%
  filter(status == 0) %>%
  group_by(rep) %>%
  filter(datetime > min(datetime, na.rm = TRUE) + 0.25 * 60 &
           datetime < max(datetime, na.rm = TRUE) - 0.25 * 60) %>% # trim start and end
  ungroup()
```

```{r data_ref_summary}
ref <- data_ref %>%
  group_by(rep) %>%
  arrange(datetime) %>%
  summarise_all(last) %>%
  mutate(cor = ref_volt / sample_volt)

cor <- ref %>%
  select(rep, cor) # use average of last minute minus trim
```

```{r data_sample}
# extract sample data
data_sample <- data_time %>%
  filter(status == 1) %>%
  left_join(cor, by = "rep") %>%
  group_by(rep) %>%
  filter(datetime > min(datetime, na.rm = TRUE) + 1 * 60 &
           datetime < max(datetime, na.rm = TRUE) - 1 * 60) %>% # trim first and last minute
  ungroup() %>%
  mutate(penetration = 100 * (cor * sample_volt) / ref_volt,
         collection = 100 - penetration)
```

```{r data_sample_summary}
# calculate summary statistics
results <- data_sample %>%
  group_by(rep) %>%
  summarise(p_max = max(penetration, na.rm = TRUE),
            c_min = min(collection, na.rm = TRUE),
            dp_initial = dp_mmh2o[which.min(datetime)],
            c_initial = collection[which.min(datetime)],
            p_initial = penetration[which.min(datetime)]) %>%
  mutate(result = if_else(c_min >= 95 & dp_initial <= 35, "PASS","FAIL")) %>%
  na.omit()
```

```{r pass_fail}
result <- if_else("FAIL" %in% results$result, "FAIL", "PASS")
```

```{r results_table_detailed}
if(params$type == "detailed"){
results_table <- results %>%
  mutate_if(is.numeric, round, 1) %>%
  mutate(p_max = cell_spec(p_max, "latex",
                           color = ifelse(p_max <= 5, "c_passed", "c_failed")),
         p_initial = cell_spec(p_initial, "latex",
                               color = ifelse(p_initial <= 5, "c_passed", "c_failed")),
         c_min = cell_spec(c_min, "latex",
                           color = ifelse(c_min >= 95, "c_passed", "c_failed")),
         c_initial = cell_spec(c_initial, "latex",
                               color = ifelse(c_initial >= 95, "c_passed", "c_failed")),
         dp_initial = cell_spec(dp_initial, "latex",
                                color = ifelse(dp_initial <= 35, "c_passed", "c_failed")),
         result = cell_spec(result, "latex",
                            color = ifelse(result == "PASS", "c_passed", "c_failed"))) %>%
  select(rep, dp_initial, p_initial, p_max, c_initial, c_min, result)
}
```

```{r results_dp_binned}
if(params$type == "binned"){
results_dp <- results %>%
  mutate(pct = if_else(dp_initial <= 35, "l1", NA_character_),
         pct = if_else(dp_initial > 35, "l2", pct),
         pct = factor(pct, levels = c("l1", "l2"))) %>%
  count(pct, .drop = FALSE) %>%
  mutate(n = if_else(n > 0, "X", "")) %>%
  pivot_wider(names_from = "pct", values_from = "n")
}
```

```{r results_table_binned}
if(params$type == "binned"){
results_table <- results %>%
  mutate(pct = if_else(c_min <= 25, "l1", NA_character_),
         pct = if_else(c_min > 25 & c_min <= 50, "l2", pct),
         pct = if_else(c_min > 50 & c_min <= 75, "l3", pct),
         pct = if_else(c_min > 75 & c_min < 95, "l4", pct),
         pct = if_else(c_min >= 95, "l5", pct),
         pct = factor(pct, levels = c("l1", "l2", "l3", "l4", "l5"))) %>%
  count(pct, .drop = FALSE) %>%
  mutate(n = if_else(n > 0, "X", "")) %>%
  pivot_wider(names_from = "pct", values_from = "n")
}
```

\vspace{-20truemm}
\begin{Large}
\begin{center}(Not for Distribution)\end{center}
\end{Large}

**Source:** `r str_to_title(meta$manufacturer[1])`

**Description:**  `r meta$description[1]` 

**Identification number:**  `r meta$id_number[1]` 

**Approval number:**  `r meta$approval[1]`

**Local supplier contact:**  `r str_to_title(meta$contact[1])`

**Intake form received:** `r if_else(meta$intake[1] == "true", "Yes", "No")`

**Date tested:**	`r as.Date(min(data$datetime))`

**Result:**	`r result`

```{r mask_image_file}
# take first matching image file
img_file <- str_subset(params$img, regex(params$id, ignore_case = TRUE))[1]
```

```{r mask_image, fig.align='center', fig.pos='h', fig.cap="A photograph of the mask/respirator that was tested.", out.width = "35%", out.extra = "angle=-90", eval = TRUE}
knitr::include_graphics(img_file, dpi=500)
```

\vspace{-5truemm}

```{r table_detailed}
if(params$type == "detailed"){
  knitr::kable(results_table, "latex", booktabs = T, escape = F, digits = 1, align = "c",
               col.names = c("Replicate", "Pressure drop (mm $H_20$)", "Initial (\\%)", "Maximum (\\%)", "Initial (\\%)", "Minimum (\\%)", "Result")) %>%
    add_header_above(c(" ", " ", "Penetration" = 2, "Removal" = 2)) %>%
    column_spec(2, width = "2.5cm") %>%
    kable_styling(latex_options = c("striped", "repeat_header"))
}
```

```{r table_binned_pen}
if(params$type == "binned"){
  kable(results_table, "latex", booktabs = T, escape = F, align = "c",
               col.names = c("0\\% to 25\\%", "25\\% to 50\\%", "50\\% to 75\\%", "75\\% to 95\\%", "maybe above 95\\%"),
               caption = "Measured particulate removal efficiency:") %>%
    kable_styling(latex_options = c("hover", "condensed", "hold_position"), full_width = F) %>%
    column_spec(1, background = "c_failed", color = "white") %>%
    column_spec(2, background = "c_failed", color = "white") %>%
    column_spec(3, background = "c_failed", color = "white") %>%
    column_spec(4, background = "c_failed", color = "white") %>%
    column_spec(5, background = "c_passed", color = "white") %>%
    row_spec(0, background = "grey50", color = "white", extra_latex_after = "\\arrayrulecolor{white}")
}
```

\vspace{-5truemm}

```{r table_binned_dp}
if(params$type == "binned"){
  kable(results_dp,
        "latex", booktabs = T, escape = F, align = "c",
        col.names = c("$\\leq$ 35 mm $H_20$", "> 35 mm $H_20$"),
        caption = "Measured pressure drop across mask or respirator:") %>%
    kable_styling(latex_options = c("condensed", "hold_position"), full_width = F) %>%
    column_spec(1, background = "c_passed", color = "white") %>%
    column_spec(2, background = "c_failed", color = "white") %>%
    row_spec(0, background = "grey50", color = "white", extra_latex_after = "\\arrayrulecolor{white}")
}
```

\vspace{-1truemm}

**Next steps:** Masks or respirators that passed this qualification test will be tested in accordance with ASTM F2100/F2266 (if a surgical mask) or NIOSH procedure TEB-APR-STP-0059-508/TEB-APR-STP-0059-007 (all other types) to confirm particulate removal efficiencies of at least 95%. Masks and respirators that did not demonstrate collection efficiencies of at least 95% during qualification testing will not undergo further testing.
